Energy and Momentum of a Density-Driven Overflow in the Samoan Passage

### 2023-02-06 reviews/response_to_reviewers.tex

\clearpage

\centerline{\bf Responses to Reviewer 2}
\vspace{0.05in}

\it 
This paper examines detailed observations and a semi-idealized 2D (non-hydrostatic) model of a density-driven overflow. The observations are impressive (i.e., they include non-trivial estimates of TKE dissipation and vertical velocities) and the authors have carefully though about how to construct energy and momentum budgets given the strengths and limitations of the observations. The modeling results do not match the observations precisely, but provide a welcomed sanity check. The paper quantifies many useful terms in the energy and momentum budgets, which will allow quantitative comparisons with future observations, numerical simulations, and parameterizations. The analyses here have significant caveats and uncertainties, but all of these issues are well documented. The manuscript is well written and references the relevant literature. Many/most references are discussed in detail and linked to the central methods and results of the study (as opposed to a less-helpful pro-forma list of references in the introduction). This work will of be of interest the readers of JPO and I recommend the paper be published with minimal edits.
\vspace{0.05in}

\bf
Thank you very much for taking the time to review the manuscript. We are glad you found the study of interest to the JPO readers.

@@

\begin{itemize}

\item \it
Fig. 9 Change the color bar on the 3rd and 4th row to match other fluxes? The purple color makes it look like the fluxes are going to the left, when compared with the rows below them.

\bf
Thank you for pointing this out. We switched the direction of the colormaps in the last three rows to match the sign of the colormap in rows 3 and 4.

### 2023-02-07 doc/northern_sill_energetics.tex

% Towyo Observations
\begin{figure*}
\centerline{\includegraphics[width=39pc]{towyo_overview.pdf}}
\caption{
Towyo-sections across the northern sill from 2012 (left) and 2014 (right).
({\bf a}) Potential temperature $\theta$ (color) and vertical velocity $w$ (black and white arrows showing upward/downward velocities, respectively, with scale given to lower right) with profile markers and a number of time stamps at top.
({\bf b}) Northward velocity $v$ (color) and $\sigma_4=45.94$\,kg\,m$^{-3}$ isopycnal tracing the upper interface (black contour).
({\bf c}) Square of vertical shear $(\partial v/\partial z)^2$ (color) and isopycnal from panel b.
({\bf d}) Turbulent dissipation $\varepsilon$ from Thorpe-scale estimates.
({\bf e}) Barotropic tide prediction \citep[TPXO,][]{egberterofeeva02} for times and locations along the section.
Note the sharp transition in measured properties and tidal phase for the 2014 section at km\,12 where the instrument had to be recovered for a few hours.
}
\label{fig:TowyoObservations}
\end{figure*}

>>>>

% Towyo Observations
\begin{figure*}
\centerline{\includegraphics[width=33pc]{towyo_overview.pdf}}
\caption{
Towyo-sections across the northern sill from 2012 (left) and 2014 (right).
({\bf a}) Potential temperature $\theta$ (color) and vertical velocity $w$ (black and white arrows showing upward/downward velocities, respectively, with scale given to lower right) with profile markers and a number of time stamps at top.
({\bf b}) Northward velocity $v$ (color) and $\sigma_4=45.94$\,kg\,m$^{-3}$ isopycnal tracing the upper interface (black contour).
({\bf c}) Vertical velocity $w$ (color) and $\sigma_4$ isopycnals at $10^{-2}$\,kg\,m$^{-3}$ intervals.
({\bf d}) Square of vertical shear $(\partial v/\partial z)^2$ (color) and isopycnals from panel c.
({\bf e}) Turbulent dissipation $\varepsilon$ from Thorpe-scale estimates.
({\bf f}) Barotropic tide prediction \citep[TPXO,][]{egberterofeeva02} for times and locations along the section.
Note the sharp transition in measured properties and tidal phase for the 2014 section at km\,12 where the instrument had to be recovered for a few hours.
}
\label{fig:TowyoObservations}
\end{figure*}
